Calendar-based graphics for visualizing people's daily schedules

### 2019-04-02 main.Rmd
added DESCRIPTION file

bibliography: bibliography.bib
output: 
  bookdown::pdf_book:
    base_format: rticles::asa_article
---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7. (\#eq:grid)
  \end{aligned}
\end{equation}

@@

```{r month-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:month-diagram-cap)"}
include_graphics("img/month.pdf")
```

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:year-diagram-cap)"}
include_graphics("img/year-diagram.pdf")
```

@@

\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c. (\#eq:final)
  \end{aligned}
\end{equation}

>>>>

bibliography: bibliography.bib
output: 
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    dev: "pdf"
---

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, out.width = "\\textwidth"
)
read_chunk('src/main.R')
```

@@

\begin{equation}
  \begin{aligned}
  i &= \lceil (g \text{ mod } 35) / 7\rceil, \\
  j &= g \text{ mod } 7.
  \end{aligned}
  (\#eq:grid)
\end{equation}

@@

```{r month-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:month-diagram-cap)"}
include_graphics("img/month.png")
```

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:year-diagram-cap)"}
include_graphics("img/year-diagram.png")
```

@@

\begin{equation}
  \begin{aligned}
  x &= j + (n - 1) \times 7 + (n - 1) \times b + h, \\
  y &= i - (m - 1) \times 5 - (m - 1) \times b + c.
  \end{aligned}
  (\#eq:final)
\end{equation}
